---
title: "Usage of ELDBR E-Resources"
author: "Alexander Harriman"
date: "2025-01-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(dplyr)
library(tidyverse)
library(gt)
library(readr)
library(readxl)
library(splitstackshape)
library(ragtop)
library(lubridate)
```



# Load Data


```{r}
eldbr <- read_excel('ELDBR List of Replaced Electronic Portfolios.xlsx')

eldbr
```



# Split up the ISBNs Into Individual Columns


```{r}
splitISBNs <- cSplit(eldbr, 'ISBN (Normalized)', ';')

splitISBNs
```



# Check the Vendors for Usage Gathering

```{r}
vendors <- eldbr |>
  group_by(`Vendor Name`) |>
  summarise(Titles = n(),
            Usage_Start_Date = min(`Portfolio Creation Date`)) |>
  arrange(`Vendor Name`)

vendors
```



Usage will need to be loaded from Cambridge, EBSCO, JSTOR, John's Hopkins Press, OUP, and ProQuest.

Use the minimum date listed for the vendor above to determine earliest usage gathering point.



# Load in Usage Data by File Type - ProQuest


```{r}
prList <- list.files(pattern = 'ProQuest-PR', full.names = TRUE)

for(i in 1:length(prList)){
  vendor <- str_split_1(prList[i], "-")[1]
  reportType <- str_split_1(prList[i], "-")[2]
  year <- substr(str_split_1(prList[i], "-")[3], 4, 7)
  datafile <- read_excel(prList[i], skip = 13) |>
    group_by(Platform, Metric_Type) |>
    summarise(Total_Usage = sum(Reporting_Period_Total)) |>
    ungroup() |>
    filter(Metric_Type == 'Unique_Item_Requests')
  assign(paste0("eldbr", vendor, reportType, year), datafile)
}


drList <- list.files(pattern = 'ProQuest-DR', full.names = TRUE)

for(i in 1:length(drList)){
  vendor <- str_split_1(drList[i], "-")[1]
  reportType <- str_split_1(drList[i], "-")[2]
  year <- substr(str_split_1(drList[i], "-")[3], 4, 7)
  datafile <- read_excel(drList[i], skip = 13) |>
    group_by(Database, Publisher, Publisher_ID, Platform, Proprietary_ID, Metric_Type) |>
    summarise(Total_Usage = sum(Reporting_Period_Total)) |>
    ungroup() |>
    filter(Metric_Type == 'Unique_Item_Requests')
  assign(paste0("eldbr", vendor, reportType, year), datafile)
}


trList <- list.files(pattern = 'ProQuest-TR', full.names = TRUE)

for(i in 1:length(trList)){
  vendor <- str_split_1(trList[i], "-")[1]
  reportType <- str_split_1(trList[i], "-")[2]
  year <- substr(str_split_1(trList[i], "-")[3], 4, 7)
  datafile <- read_excel(trList[i], skip = 13) |>
    group_by(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, ISBN, Print_ISSN, Online_ISSN, URI, Metric_Type) |>
    summarise(Total_Usage = sum(Reporting_Period_Total)) |>
    ungroup() |>
    filter(Metric_Type == 'Unique_Item_Requests')    
  assign(paste0("eldbr", vendor, reportType, year), datafile)
}
```




# Join the Files Together

```{r}
# DR
proQuest_dr_mid <- full_join(`eldbr./ProQuestDR2022`, `eldbr./ProQuestDR2023`, by = c('Database', 'Publisher', 'Publisher_ID', 'Platform', 'Proprietary_ID', 'Metric_Type'))
proQuestDR <- full_join(proQuest_dr_mid, `eldbr./ProQuestDR2024`, by = c('Database', 'Publisher', 'Publisher_ID', 'Platform', 'Proprietary_ID', 'Metric_Type')) |>
  select(Database, Publisher, Publisher_ID, Platform, Proprietary_ID, Metric_Type, Total_Usage)


# PR
proQuest_pr_mid <- full_join(`eldbr./ProQuestPR2022`, `eldbr./ProQuestPR2023`, by = c('Platform', 'Metric_Type'))
proQuestPR <- full_join(proQuest_pr_mid, `eldbr./ProQuestPR2024`, by = c('Platform', 'Metric_Type')) |>
  select(Platform, Metric_Type, Total_Usage)
  
  
# TR
proQuest_tr_mid <- full_join(`eldbr./ProQuestTR2022`, `eldbr./ProQuestTR2023`, by = c('Title', 'Publisher', 'Publisher_ID', 'Platform', 'DOI', 'Proprietary_ID', 'ISBN', 'Print_ISSN', 'Online_ISSN', 'URI', 'Metric_Type'))
proQuestTR <- full_join(proQuest_tr_mid, `eldbr./ProQuestTR2024`, by = c('Title', 'Publisher', 'Publisher_ID', 'Platform', 'DOI', 'Proprietary_ID', 'ISBN', 'Print_ISSN', 'Online_ISSN', 'URI', 'Metric_Type'))  |>
  select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, ISBN, Print_ISSN, Online_ISSN, URI, Metric_Type, Total_Usage)
```




# Load in Usage Data by File Type - Other Vendors


```{r}
prList <- grep(list.files(pattern = 'PR', full.names = TRUE), pattern = 'ProQuest-', invert = TRUE, value = TRUE)

for(i in 1:length(prList)){
  vendor <- str_split_1(prList[i], "-")[1]
  reportType <- str_split_1(prList[i], "-")[2]
  datafile <- read_tsv(prList, skip = 13, show_col_types = FALSE) |>
    filter(Metric_Type == 'Unique_Item_Requests') |>
    mutate(Total_Usage = Reporting_Period_Total) |>
    select(Platform, Metric_Type, Total_Usage)
  assign(paste0("eldbr", vendor, reportType), datafile)
}


drList <- grep(list.files(pattern = 'DR', full.names = TRUE), pattern = 'ProQuest-', invert = TRUE, value = TRUE)

for(i in 1:length(drList)){
  vendor <- str_split_1(drList[i], "-")[1]
  reportType <- str_split_1(drList[i], "-")[2]
  datafile <- read_tsv(drList, skip = 13, show_col_types = FALSE) |>
    filter(Metric_Type == 'Unique_Item_Requests') |>
    mutate(Total_Usage = Reporting_Period_Total) |>
    select(Database, Publisher, Publisher_ID, Platform, Proprietary_ID, Metric_Type, Total_Usage)
  assign(paste0("eldbr", vendor, reportType), datafile)
}


trList <- grep(list.files(pattern = 'TR', full.names = TRUE), pattern = 'ProQuest-', invert = TRUE, value = TRUE)

for(i in 1:length(trList)){
  vendor <- str_split_1(trList[i], "-")[1]
  reportType <- str_split_1(trList[i], "-")[2]
  datafile <- read_tsv(trList, skip = 13, show_col_types = FALSE) |>
    filter(Metric_Type == 'Unique_Item_Requests') |>
    mutate(Total_Usage = Reporting_Period_Total) |>
    select(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, ISBN, Print_ISSN, Online_ISSN, URI, Metric_Type, Total_Usage)
  assign(paste0("eldbr", vendor, reportType), datafile)
}
```





# Combine Like File Types


```{r}
PR <- rbind(`eldbr./CambridgePR`, `eldbr./EBSCOPR`, `eldbr./JSTORPR`, `eldbr./OUPPR`, `eldbr./ProQuestEBooksPR`, proQuestPR)

DR <- rbind(`eldbr./EBSCODR`, `eldbr./JSTORDR`, `eldbr./OUPDR`, proQuestDR)

TR <- rbind(`eldbr./CambridgeTR`, `eldbr./EBSCOTR`, `eldbr./JSTORTR`, `eldbr./OUPTR`, `eldbr./ProQuestEBooksTR`, proQuestTR)
```




```{r}
TR
splitISBNs
```




# Normalize the ISBNs




```{r}
cleanTR <- TR |>
  mutate(ISBN = gsub("-", "", ISBN)) |>
  distinct(.keep_all = TRUE)

cleanTR
```



# Attempt the Title Cleanup From the ILL Report



```{r}
for(i in 1:dim(cleanTR)[1]){
  cleanTR$cleanTitle[i] <- tolower(gsub("[[:punct:]]", "", str_split(cleanTR$Title[i], '\\*')[[1]][1]))
  cleanTR$keyWord1[i] <- ifelse(is.na(str_split(cleanTR$cleanTitle[i], ' ')[[1]][1]) == TRUE, '',
                                      str_split(cleanTR$cleanTitle[i], ' ')[[1]][1])
  cleanTR$keyWord2[i] <- ifelse(is.na(str_split(cleanTR$cleanTitle[i], ' ')[[1]][2]) == TRUE, '',
                                      str_split(cleanTR$cleanTitle[i], ' ')[[1]][2])
  cleanTR$keyWord3[i] <- ifelse(is.na(str_split(cleanTR$cleanTitle[i], ' ')[[1]][3]) == TRUE, '',
                                      str_split(cleanTR$cleanTitle[i], ' ')[[1]][3])
  cleanTR$keyWord4[i] <- ifelse(is.na(str_split(cleanTR$cleanTitle[i], ' ')[[1]][4]) == TRUE, '',
                                      str_split(cleanTR$cleanTitle[i], ' ')[[1]][4])
}
```




# Do the same Cleanup for the Alma Report


```{r}
for(i in 1:dim(splitISBNs)[1]){
  splitISBNs$cleanTitle[i] <- tolower(gsub("[[:punct:]]", "", str_split(splitISBNs$Title[i], '\\*')[[1]][1]))
  splitISBNs$keyWord1[i] <- ifelse(is.na(str_split(splitISBNs$cleanTitle[i], ' ')[[1]][1]) == TRUE, '',
                                      str_split(splitISBNs$cleanTitle[i], ' ')[[1]][1])
  splitISBNs$keyWord2[i] <- ifelse(is.na(str_split(splitISBNs$cleanTitle[i], ' ')[[1]][2]) == TRUE, '',
                                      str_split(splitISBNs$cleanTitle[i], ' ')[[1]][2])
  splitISBNs$keyWord3[i] <- ifelse(is.na(str_split(splitISBNs$cleanTitle[i], ' ')[[1]][3]) == TRUE, '',
                                      str_split(splitISBNs$cleanTitle[i], ' ')[[1]][3])
  splitISBNs$keyWord4[i] <- ifelse(is.na(str_split(splitISBNs$cleanTitle[i], ' ')[[1]][4]) == TRUE, '',
                                      str_split(splitISBNs$cleanTitle[i], ' ')[[1]][4])
}
```



```{r}
for(i in 1:dim(eldbr)[1]){
  eldbr$cleanTitle[i] <- tolower(gsub("[[:punct:]]", "", str_split(eldbr$Title[i], '\\*')[[1]][1]))
  eldbr$keyWord1[i] <- ifelse(is.na(str_split(eldbr$cleanTitle[i], ' ')[[1]][1]) == TRUE, '',
                                      str_split(eldbr$cleanTitle[i], ' ')[[1]][1])
  eldbr$keyWord2[i] <- ifelse(is.na(str_split(eldbr$cleanTitle[i], ' ')[[1]][2]) == TRUE, '',
                                      str_split(eldbr$cleanTitle[i], ' ')[[1]][2])
  eldbr$keyWord3[i] <- ifelse(is.na(str_split(eldbr$cleanTitle[i], ' ')[[1]][3]) == TRUE, '',
                                      str_split(eldbr$cleanTitle[i], ' ')[[1]][3])
  eldbr$keyWord4[i] <- ifelse(is.na(str_split(eldbr$cleanTitle[i], ' ')[[1]][4]) == TRUE, '',
                                      str_split(eldbr$cleanTitle[i], ' ')[[1]][4])
}
```



# Combine the Words and Attempt to Join


```{r}
titleSplitAlma <- eldbr |>
  mutate(mainTitle = paste0(keyWord1, keyWord2, keyWord3, keyWord4))


titleSplitUsage <- cleanTR |>
  mutate(mainTitle = paste0(keyWord1, keyWord2, keyWord3, keyWord4))



firstStep <- inner_join(titleSplitAlma, titleSplitUsage, by = 'mainTitle') 

firstStep <- firstStep |>
  mutate(Title.y = ifelse(Title.y == 'Statistical mechanics', 'Statistical Mechanics', Title.y))


firstStep
```




# Clean Up the First Step


```{r}
usageA <- firstStep |>
  group_by(Title.y, `ISBN (Normalized)`, `Portfolio Creation Date`, `MMS Id`, Cost) |>
  summarise(Reporting_Period_Total = sum(Total_Usage)) |>
  ungroup() |>
  mutate(Title = Title.y) |>
  select(Title, `ISBN (Normalized)`, `MMS Id`, `Portfolio Creation Date`, Reporting_Period_Total, Cost)

usageA
```




# Check the Final Titles Currently Without Usage


```{r}
noUse <- left_join(titleSplitAlma, titleSplitUsage, by = 'mainTitle') |>
  filter(is.na(Total_Usage) == TRUE)


noUse
```


# ISBN Join Check

```{r}
noUseSplit <- cSplit(noUse, 'ISBN (Normalized)', ';') |>
  mutate(`ISBN (Normalized)_01` = as.character(`ISBN (Normalized)_01`),
         `ISBN (Normalized)_03` = as.character(`ISBN (Normalized)_03`),
         `ISBN (Normalized)_05` = as.character(`ISBN (Normalized)_05`),
         `ISBN (Normalized)_06` = as.character(`ISBN (Normalized)_06`),
         `ISBN (Normalized)_07` = as.character(`ISBN (Normalized)_07`),
         `ISBN (Normalized)_08` = as.character(`ISBN (Normalized)_08`),
         `ISBN (Normalized)_09` = as.character(`ISBN (Normalized)_09`),
         `ISBN (Normalized)_10` = as.character(`ISBN (Normalized)_10`),
         `ISBN (Normalized)_11` = as.character(`ISBN (Normalized)_11`),
         `ISBN (Normalized)_12` = as.character(`ISBN (Normalized)_12`))

noUseSplit
```





# Check Usage Reports


```{r}
secondStep <- cleanTR |>
  filter(is.na(ISBN) == FALSE) |>
  filter(ISBN %in% noUseSplit$`ISBN (Normalized)_01` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_02` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_03` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_04` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_05` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_06` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_07` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_08` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_09` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_10` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_11` |
           ISBN %in% noUseSplit$`ISBN (Normalized)_12`) |>
  mutate(mainTitle = paste0(keyWord1, keyWord2, keyWord3, keyWord4))

secondStep$Cost <- c(61.88, 171.83, 149, 29.39, 39.69, 36.75, 47.04)

secondStep$`Portfolio Creation Date` <- c(as.POSIXct('2021-08-10'), as.POSIXct('2024-01-17'), as.POSIXct('2023-10-12'), as.POSIXct('2023-10-12'), as.POSIXct('2023-02-03'), as.POSIXct('2023-01-26'), as.POSIXct('2023-04-18'))

secondStep$`MMS Id` <- c('9926062147002311', '9926478723502311', '9926415751002311', '9926415519502311', '9926311783302311', '9926310422702311', '9926342384202311')

secondStep
```




# Clean Up the Second Step


```{r}
usageB <- secondStep |>
  group_by(Title, `ISBN`, `MMS Id`, `Portfolio Creation Date`, Cost) |>
  summarise(Reporting_Period_Total = sum(Total_Usage)) |>
  ungroup() |>
  select(Title, `ISBN`, `MMS Id`, `Portfolio Creation Date`, Reporting_Period_Total, Cost)

colnames(usageB) <- c('Title', 'ISBN (Normalized)', 'MMS Id', 'Portfolio Creation Date', 'Reporting_Period_Total', 'Cost')

usageB
```


# Get the Rest of the No Usage Titles


```{r}
noUseSplit2 <- noUseSplit |>
  filter(!keyWord1.x %in% secondStep$keyWord1) |>
  filter(mainTitle != 'themoralityofdrone')

noUseSplit2
```




```{r}
noUseRestart <- eldbr |>
  filter(Title %in% noUseSplit2$Title.x)


noUseRestart
```



# Remove All Articles From Titles and Re-Start the Title Joining



```{r}
cleanTR2 <- cleanTR


for(i in 1:dim(cleanTR2)[1]){
  firstTitleClean <- tolower(gsub("[[:punct:]]", "", str_split(cleanTR2$Title[i], '\\*')[[1]][1]))
  for(word in c('and', 'a', 'the', 'The', 'A', 'And', 'to', 'of')){
      firstTitleClean <- str_remove_all(firstTitleClean, paste0("\\b", word, "\\b"))
  }


  splitTitle <- str_split(firstTitleClean, ' ')[[1]]

  
  removeList <- c()
  for(j in 1:length(splitTitle)){
    if(is.blank(splitTitle[j]) == TRUE){
      removeList <- append(removeList, j)
    }
  }
  
  
  if(is.null(removeList) == TRUE){
    finalSplit <- splitTitle
  }
  else{
    finalSplit <- splitTitle[-removeList]
  }

  
  cleanTR2$keyWord1[i] <- finalSplit[1]
  cleanTR2$keyWord2[i] <- ifelse(is.na(finalSplit[2]) == TRUE, '', finalSplit[2])
  cleanTR2$keyWord3[i] <- ifelse(is.na(finalSplit[3]) == TRUE, '', finalSplit[3])
  cleanTR2$keyWord4[i] <- ifelse(is.na(finalSplit[4]) == TRUE, '', finalSplit[4])
  
  cleanTR2$cleanTitle[i] <- paste0(finalSplit[1], 
                                       ifelse(is.na(finalSplit[2]) == TRUE, '', finalSplit[2]), 
                                       ifelse(is.na(finalSplit[3]) == TRUE, '', finalSplit[3]), 
                                       ifelse(is.na(finalSplit[4]) == TRUE, '', finalSplit[4]))
}

cleanTR2
```


```{r}
for(i in 1:dim(noUseRestart)[1]){
  firstTitleClean <- tolower(gsub("[[:punct:]]", "", str_split(noUseRestart$Title[i], '\\*')[[1]][1]))
  for(word in c('and', 'a', 'the', 'The', 'A', 'And', 'to', 'of')){
      firstTitleClean <- str_remove_all(firstTitleClean, paste0("\\b", word, "\\b"))
  }


  splitTitle <- str_split(firstTitleClean, ' ')[[1]]

  
  removeList <- c()
  for(j in 1:length(splitTitle)){
    if(is.blank(splitTitle[j]) == TRUE){
      removeList <- append(removeList, j)
    }
  }
  
  
  if(is.null(removeList) == TRUE){
    finalSplit <- splitTitle
  }
  else{
    finalSplit <- splitTitle[-removeList]
  }

  
  noUseRestart$keyWord1[i] <- finalSplit[1]
  noUseRestart$keyWord2[i] <- ifelse(is.na(finalSplit[2]) == TRUE, '', finalSplit[2])
  noUseRestart$keyWord3[i] <- ifelse(is.na(finalSplit[3]) == TRUE, '', finalSplit[3])
  noUseRestart$keyWord4[i] <- ifelse(is.na(finalSplit[4]) == TRUE, '', finalSplit[4])
  
  noUseRestart$cleanTitle[i] <- paste0(finalSplit[1], 
                                       ifelse(is.na(finalSplit[2]) == TRUE, '', finalSplit[2]), 
                                       ifelse(is.na(finalSplit[3]) == TRUE, '', finalSplit[3]), 
                                       ifelse(is.na(finalSplit[4]) == TRUE, '', finalSplit[4]))
}

noUseRestart
```



# Join the Two Files



```{r}
thirdStep <- inner_join(noUseRestart, cleanTR2, by = 'cleanTitle')

thirdStep
```







# Manually Find the Final Usage Information




```{r}
noUseRestart
```



```{r}
almostFinalStep <- data.frame(
  Title = c('Forecasting, Structural Time Series Models and the Kalman Filter',
            'A Shameful Life', 
            'Introduction to Quantum Mechanics', 
            'Teaching Social Studies That Matters', 
            'Politics and Government in the Middle East and North Africa',
            'The Oromo Movement and Imperial Politics',
            "Thomas Piketty's 'Capital in the Twenty First Century': An Introduction",
            'The Poetics of Ruins in Renaissance Literature',
            'Rationality and the Reflective Mind',
            'Boredom, Architecture and Spatial Experience',
            'Butterfly Boy',
            'Dietland',
            'Gender Epistemologies in Africa',
            'Imagined Communities',
            'Introduction to Soft Matter',
            'Sonidos en Contexto',
            'State Lotteries and Legalized Gambling: Painless Revenue or Painful Mirage',
            'Stochastic Models in Biology',
            'The Berlin Wall Crisis',
            'The Dresden Firebombing'),
  `ISBN (Normalized)` = noUseRestart$`ISBN (Normalized)`,
  `MMS Id` = noUseRestart$`MMS Id`,
  `Portfolio Creation Date` = noUseRestart$`Portfolio Creation Date`,
  Reporting_Period_Total = c(0,
                             0, 
                             0, 
                             0,
                             1,
                             0,
                             0,
                             0,
                             0,
                             0,
                             0,
                             0,
                             0,
                             17,
                             0,
                             0,
                             0,
                             0,
                             0,
                             0),
  Cost = noUseRestart$Cost
)

colnames(almostFinalStep) <- c('Title', 'ISBN (Normalized)', 'MMS Id', 'Portfolio Creation Date', 'Reporting_Period_Total', 'Cost')

almostFinalStep
```


# Combine All Usage

```{r}
allUsage <- rbind(usageA, usageB, almostFinalStep)

allUsage
```




# Get the Current No Usage Items And Double-Check Vendors in Alma


```{r}
noUsage <- allUsage |>
  filter(Reporting_Period_Total < 1)

noUsage
```


Vendors That Need to Be Accounted For:


* Kalman Confirmed in Cambridge, no usage.
* A Shameful Life Confirmed in EBSCO, no usage.
* Introduction to Quantum Mechanics is on **Knovel**, but Knovel has no title-based usage. With nothing on EBSCO, this is listed as a no usage.
* Teaching Social Studies that Matters Confirmed in EBSCO, no usage.
* The Oromo Movement Confirmed in EBSCO, no usage.
* Thomas Piketty Confirmed in EBSCO, no usage.
* Poetics of Ruins is on **Project MUSE**. However, it has no usage.
* Rationality and the Reflective Mind Confirmed in OUP, no usage.
* Boredom Confirmed in ProQuest, no usage.
* Butterfly Boy Confirmed in ProQuest, no usage.
* Dietland Confirmed in ProQuest, no usage.
* Gender Epistemologies Confirmed in ProQuest, no usage.
* Soft Matter Confirmed in ProQuest, no usage.
* Sonidos Confirmed in ProQuest, no usage.
* State Lotteries Confirmed in ProQuest, no usage.
* Stochastic Models Confirmed in ProQuest, no usage.
* Berlin Wall Crisis Confirmed in ProQuest, no usage.
* Dresden Confirmed in ProQuest, no usage.






# Add the Vendor to the Final Outcome


```{r}
usageVendor <- left_join(allUsage, eldbr, by = 'ISBN (Normalized)') |>
  select(Title.x, `ISBN (Normalized)`, `MMS Id.x`, `Portfolio Creation Date.x`, `Vendor Name`, Reporting_Period_Total, Cost.x)

colnames(usageVendor) <- c('Title', 'ISBN', 'MMS ID', 'Portfolio Creation Date', 'Vendor Name', 'Total_Usage', 'Cost')


# Fill in Gaps

filledGaps <- usageVendor |>
  mutate(ISBN = case_when(
    Title == 'Circuit-Bending' ~ '0471752959; 9780471752950; 9780764588877; 0764588877',
    Title == 'Colonial Botany' ~ '9780812293470; 0812293479; 9780812220094; 0812220099',
    Title == 'Ghost Wars: The Secret History of the CIA, Afghanistan, and Bin Laden, From the Soviet Invasion to September 10, 2001 (Pulitzer Prize Winner)' ~ '1429513659; 9781429513654; 1429521007; 9781429521000; 1101221437; 9781101221433; 0141935790; 9780141935799; 9780143034667; 0143034669; 9780141020808; 0141020806',
    Title == 'Legitimacy Gap: Secularism, Religion, and Culture in Comparative Constitutional Law' ~ '0192528270; 9780192528278; 0198803826; 9780198803829',
    Title == 'Morality of Drone Warfare and the Politics of Regulation.' ~ '1137533803; 9781137533807; 9781137533791; 113753379X',
    Title == 'Undesirables' ~ '1503633705; 9781503633704; 9781503632912; 1503632911',
    Title == 'Young Adult Literature, Fourth Edition' ~ '9780838937471; 0838937470; 9780838937488; 0838937489; 9780838947470; 0838947476',
    .default = ISBN
  ),
  `Vendor Name` = case_when(
    Title == 'Circuit-Bending' ~ 'ProQuest LLC',
    Title == 'Colonial Botany' ~ 'ProQuest LLC',
    Title == 'Ghost Wars: The Secret History of the CIA, Afghanistan, and Bin Laden, From the Soviet Invasion to September 10, 2001 (Pulitzer Prize Winner)' ~ 'EBSCO INFORMATION SERVICES',
    Title == 'Legitimacy Gap: Secularism, Religion, and Culture in Comparative Constitutional Law' ~ 'EBSCO INFORMATION SERVICES',
    Title == 'Morality of Drone Warfare and the Politics of Regulation.' ~ 'EBSCO INFORMATION SERVICES',
    Title == 'Undesirables' ~ 'ProQuest LLC',
    Title == 'Young Adult Literature, Fourth Edition' ~ 'ProQuest LLC',
    .default = `Vendor Name`    
  )
  )


filledGaps
```






# Focus on Usage Only Since Re-Purchase


# Get All 0 Usage Titles


```{r}
lackUse <- filledGaps |>
  filter(Total_Usage == 0)


lackUse
```


# Load in All Non-ProQuest Titles Again

```{r}
trList <- grep(list.files(pattern = 'TR', full.names = TRUE), pattern = 'ProQuest-', invert = TRUE, value = TRUE)

for(i in 1:length(trList)){
  vendor <- str_split_1(trList[i], "-")[1]
  reportType <- str_split_1(trList[i], "-")[2]
  datafile <- read_tsv(trList, skip = 13, show_col_types = FALSE) |>
    filter(Metric_Type == 'Unique_Item_Requests') |>
    mutate(Total_Usage = Reporting_Period_Total)
  assign(paste0("eldbr", vendor, reportType, 'and_months'), datafile)
}
```





# Load in Usage Data by File Type - ProQuest


```{r}
trList <- list.files(pattern = 'ProQuest-TR', full.names = TRUE)

for(i in 1:length(trList)){
  vendor <- str_split_1(trList[i], "-")[1]
  reportType <- str_split_1(trList[i], "-")[2]
  year <- substr(str_split_1(trList[i], "-")[3], 4, 7)
  datafile <- read_excel(trList[i], skip = 13) |>
    filter(Metric_Type == 'Unique_Item_Requests')    
  assign(paste0("eldbr", vendor, reportType, year, '_and_months'), datafile)
}
```




# Join the Files Together

```{r}
# TR
proQuestTRMonths <- plyr::rbind.fill(`eldbr./ProQuestTR2022_and_months`, `eldbr./ProQuestTR2023_and_months`, `eldbr./ProQuestTR2024_and_months`)
```




```{r}
proQuestTRMonths2 <- proQuestTRMonths |>
  group_by(Title, Publisher, Publisher_ID, Platform, DOI, Proprietary_ID, ISBN, Print_ISSN, Online_ISSN, URI, Metric_Type) |>
  summarise(Reporting_Period_Total = sum(Reporting_Period_Total, na.rm = TRUE),
            `Jan-2022` = sum(`44562`, na.rm = TRUE),
            `Feb-2022` = sum(`44593`, na.rm = TRUE),
            `Mar-2022` = sum(`44621`, na.rm = TRUE),
            `Apr-2022` = sum(`44652`, na.rm = TRUE),
            `May-2022` = sum(`44682`, na.rm = TRUE),
            `Jun-2022` = sum(`44713`, na.rm = TRUE),
            `Jul-2022` = sum(`44743`, na.rm = TRUE),
            `Aug-2022` = sum(`44774`, na.rm = TRUE),
            `Sep-2022` = sum(`44805`, na.rm = TRUE),
            `Oct-2022` = sum(`44835`, na.rm = TRUE),
            `Nov-2022` = sum(`44866`, na.rm = TRUE),
            `Dec-2022` = sum(`44896`, na.rm = TRUE),
            `Jan-2023` = sum(`44927`, na.rm = TRUE),
            `Feb-2023` = sum(`44958`, na.rm = TRUE),
            `Mar-2023` = sum(`44986`, na.rm = TRUE),
            `Apr-2023` = sum(`45017`, na.rm = TRUE),
            `May-2023` = sum(`45047`, na.rm = TRUE),
            `Jun-2023` = sum(`45078`, na.rm = TRUE),
            `Jul-2023` = sum(`45108`, na.rm = TRUE),
            `Aug-2023` = sum(`45139`, na.rm = TRUE),
            `Sep-2023` = sum(`45170`, na.rm = TRUE),
            `Oct-2023` = sum(`45200`, na.rm = TRUE),
            `Nov-2023` = sum(`45231`, na.rm = TRUE),
            `Dec-2023` = sum(`45261`, na.rm = TRUE),
            `Jan-2024` = sum(`Jan-24`, na.rm = TRUE),
            `Feb-2024` = sum(`Feb-24`, na.rm = TRUE),
            `Mar-2024` = sum(`Mar-24`, na.rm = TRUE),
            `Apr-2024` = sum(`Apr-24`, na.rm = TRUE),
            `May-2024` = sum(`May-24`, na.rm = TRUE),
            `Jun-2024` = sum(`Jun-24`, na.rm = TRUE),
            `Jul-2024` = sum(`Jul-24`, na.rm = TRUE),
            `Aug-2024` = sum(`Aug-24`, na.rm = TRUE),
            `Sep-2024` = sum(`Sep-24`, na.rm = TRUE),
            `Oct-2024` = sum(`Oct-24`, na.rm = TRUE),
            `Nov-2024` = sum(`Nov-24`, na.rm = TRUE),
            `Dec-2024` = sum(`Dec-24`, na.rm = TRUE),
            `Total_Usage` = sum(Reporting_Period_Total, na.rm = TRUE)
            ) |>
  ungroup()



proQuestTRMonths2
```



```{r}
TRMonths <- rbind(`eldbr./CambridgeTRand_months`, `eldbr./EBSCOTRand_months`, `eldbr./JSTORTRand_months`, `eldbr./OUPTRand_months`, `eldbr./ProQuestEBooksTRand_months`, proQuestTRMonths2)
```





# Get Titles with Usage


```{r}
withUse <- filledGaps |>
  filter(Total_Usage > 0)


withUse
```


# Join the Monthly Usage to the Final Usage

```{r}
withMonths <- inner_join(withUse, TRMonths, by = 'Title') |>
  distinct()

withMonths
```




# Filter Out Duplicates by ISBN



```{r}
filteredMonths <- withMonths |>
  filter(!ISBN.y %in% c('978-0-12-382188-1', '978-1-56368-043-4')) |>
  filter(Platform != 'Oxford Academic' | ISBN.y != '978-0-19-960868-3')


filteredMonths
```




# Gather Usage Based on Portfolio Date


```{r}
fromBuyUsage <- filteredMonths |>
  mutate(usageSincePurchase = 
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-02-01'), 0, `Jan-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-03-01'), 0, `Feb-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-04-01'), 0, `Mar-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-04-01'), 0, `Apr-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-06-01'), 0, `May-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-07-01'), 0, `Jun-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-08-01'), 0, `Jul-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-09-01'), 0, `Aug-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-10-01'), 0, `Sep-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-11-01'), 0, `Oct-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2022-12-01'), 0, `Nov-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-01-01'), 0, `Dec-2022`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-02-01'), 0, `Jan-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-03-01'), 0, `Feb-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-04-01'), 0, `Mar-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-05-01'), 0, `Apr-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-06-01'), 0, `May-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-07-01'), 0, `Jun-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-08-01'), 0, `Jul-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-09-01'), 0, `Aug-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-10-01'), 0, `Sep-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-11-01'), 0, `Oct-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2023-12-01'), 0, `Nov-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-01-01'), 0, `Dec-2023`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-02-01'), 0, `Jan-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-03-01'), 0, `Feb-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-04-01'), 0, `Mar-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-05-01'), 0, `Apr-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-06-01'), 0, `May-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-07-01'), 0, `Jun-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-08-01'), 0, `Jul-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-09-01'), 0, `Aug-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-10-01'), 0, `Sep-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-11-01'), 0, `Oct-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2024-12-01'), 0, `Nov-2024`) +
      ifelse(`Portfolio Creation Date` > as.POSIXct('2025-01-01'), 0, `Dec-2024`)
  ) |>
  mutate(usageFirstSix = case_when(
        between(`Portfolio Creation Date`, as.POSIXct('2022-01-01'), as.POSIXct('2022-02-01')) ~ `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-02-01'), as.POSIXct('2022-03-01')) ~ `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-03-01'), as.POSIXct('2022-04-01')) ~ `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-04-01'), as.POSIXct('2022-05-01')) ~ `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-05-01'), as.POSIXct('2022-06-01')) ~ `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-06-01'), as.POSIXct('2022-07-01')) ~ `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-07-01'), as.POSIXct('2022-08-01')) ~ `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-08-01'), as.POSIXct('2022-09-01')) ~ `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-09-01'), as.POSIXct('2022-10-01')) ~ `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-10-01'), as.POSIXct('2022-11-01')) ~ `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-11-01'), as.POSIXct('2022-12-01')) ~ `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-12-01'), as.POSIXct('2023-01-01')) ~ `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-01-01'), as.POSIXct('2023-02-01')) ~ `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-02-01'), as.POSIXct('2023-03-01')) ~ `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-03-01'), as.POSIXct('2023-04-01')) ~ `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-04-01'), as.POSIXct('2023-05-01')) ~ `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-05-01'), as.POSIXct('2023-06-01')) ~ `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-06-01'), as.POSIXct('2023-07-01')) ~ `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-07-01'), as.POSIXct('2023-08-01')) ~ `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-08-01'), as.POSIXct('2023-09-01')) ~ `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-09-01'), as.POSIXct('2023-10-01')) ~ `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-10-01'), as.POSIXct('2023-11-01')) ~ `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-11-01'), as.POSIXct('2023-12-01')) ~ `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-12-01'), as.POSIXct('2024-01-01')) ~ `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2024-01-01'), as.POSIXct('2024-02-01')) ~ `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2024-02-01'), as.POSIXct('2024-03-01')) ~ `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2024-03-01'), as.POSIXct('2024-04-01')) ~ `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2024-04-01'), as.POSIXct('2024-05-01')) ~ `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2024-05-01'), as.POSIXct('2024-06-01')) ~ `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2024-06-01'), as.POSIXct('2024-07-01')) ~ `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024`,
    .default = `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`
  )
    ) |>
  mutate(usageFirstYear = case_when(
        between(`Portfolio Creation Date`, as.POSIXct('2022-01-01'), as.POSIXct('2022-02-01')) ~ 
          `Jan-2022` + `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-02-01'), as.POSIXct('2022-03-01')) ~ 
          `Feb-2022` + `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-03-01'), as.POSIXct('2022-04-01')) ~ 
          `Mar-2022` + `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-04-01'), as.POSIXct('2022-05-01')) ~ 
          `Apr-2022` + `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-05-01'), as.POSIXct('2022-06-01')) ~ 
          `May-2022` + `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-06-01'), as.POSIXct('2022-07-01')) ~ 
          `Jun-2022` + `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-07-01'), as.POSIXct('2022-08-01')) ~ 
          `Jul-2022` + `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-08-01'), as.POSIXct('2022-09-01')) ~ 
          `Aug-2022` + `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-09-01'), as.POSIXct('2022-10-01')) ~ 
          `Sep-2022` + `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-10-01'), as.POSIXct('2022-11-01')) ~ 
          `Oct-2022` + `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-11-01'), as.POSIXct('2022-12-01')) ~ 
          `Nov-2022` + `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2022-12-01'), as.POSIXct('2023-01-01')) ~ 
          `Dec-2022` + `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-01-01'), as.POSIXct('2023-02-01')) ~ 
          `Jan-2023` + `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-02-01'), as.POSIXct('2023-03-01')) ~ 
          `Feb-2023` + `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-03-01'), as.POSIXct('2023-04-01')) ~ 
          `Mar-2023` + `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-04-01'), as.POSIXct('2023-05-01')) ~ 
          `Apr-2023` + `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-05-01'), as.POSIXct('2023-06-01')) ~ 
          `May-2023` + `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-06-01'), as.POSIXct('2023-07-01')) ~ 
          `Jun-2023` + `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-07-01'), as.POSIXct('2023-08-01')) ~ 
          `Jul-2023` + `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-08-01'), as.POSIXct('2023-09-01')) ~ 
          `Aug-2023` + `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-09-01'), as.POSIXct('2023-10-01')) ~ 
          `Sep-2023` + `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-10-01'), as.POSIXct('2023-11-01')) ~ 
          `Oct-2023` + `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-11-01'), as.POSIXct('2023-12-01')) ~ 
          `Nov-2023` + `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024`,
        between(`Portfolio Creation Date`, as.POSIXct('2023-12-01'), as.POSIXct('2024-01-01')) ~ 
          `Dec-2023` + `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024`,
    .default = `Jan-2024` + `Feb-2024` + `Mar-2024` + `Apr-2024` + `May-2024` + `Jun-2024` + `Jul-2024` + `Aug-2024` + `Sep-2024` + `Oct-2024` + `Nov-2024` + `Dec-2024`
  )
    ) |>
  select(Title, ISBN.x, `MMS ID`, `Portfolio Creation Date`, `Vendor Name`, usageFirstSix, usageFirstYear, usageSincePurchase, Cost)


colnames(fromBuyUsage) <- c('Title', 'ISBN', 'MMS ID', 'Portfolio Creation Date', 'Vendor Name', 'First_Six_Usage', 'First_Year_Usage', 'Total_Usage', 'Cost')


fromBuyUsage
```



# Combine the No Usage and Some Usage Tables



```{r}
lackUseNew <- lackUse |>
  mutate(First_Six_Usage = 0,
         First_Year_Usage = 0) |>
  select(Title, ISBN, `MMS ID`, `Portfolio Creation Date`, `Vendor Name`, First_Six_Usage, First_Year_Usage, Total_Usage, Cost)


lackUseNew
```



```{r}
finalTable <- rbind(fromBuyUsage, lackUseNew)

finalTable
```




# Calculate Cost Per Use



```{r}
costUse <- finalTable |>
  mutate(numMonths = ifelse(`Portfolio Creation Date` < as.POSIXct('2022-01-01'), 36,
                            interval(`Portfolio Creation Date`, Sys.Date()) %/% months(1))) |>
  mutate(usagePerYear = (12 * Total_Usage) / numMonths) |>
  mutate(`Cost/Use` = round(ifelse(usagePerYear == 0, NA_real_, Cost / usagePerYear), 2),
         `Total Cost` = round(Cost, 2),
         `Usage/Yr` = round(usagePerYear, 1),
         `Total Usage` = Total_Usage) |>
  mutate(costUseBucket = case_when(
    `Total Usage` == 0 ~ 'No Loans',
    `Cost/Use` < 20 ~ 'Under $20',
    `Cost/Use` >= 20 ~ 'Over $20',
    .default = NA
  )) |>
  select(Title, ISBN, `MMS ID`, `Portfolio Creation Date`, First_Six_Usage, First_Year_Usage, `Total Usage`, `Total Cost`, `Usage/Yr`, `Cost/Use`, costUseBucket)


costUse
```




# Export the Files


```{r}
write.csv(costUse, 'Cost Per Use of ELDBR E-Resource Replacements.csv', row.names = FALSE)
```



