---
title: "OUP Overlap Usage in Other Vendors"
author: "Alexander Harriman"
date: "2024-11-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(plyr)
library(readr)
library(dplyr)
library(tidyverse)
library(readxl)
library(ggplot2)
library(plotly)
library(gt)
```


# Load Data


```{r}
overlap <- read_excel('OUP Titles with Complete Overlap with Other Vendors.xlsx')

overlap
```


# Figure out which Interfaces Most Overlap Occurs In


```{r}
fullOverlapList <- vector()

for(i in 1:dim(overlap)[1]){
  allVendors <- strsplit(overlap$`Interface - Target Set`[i], split = '\"}\r\n\r\n{\"', fixed = TRUE)
  number <- length(allVendors[[1]])
  
  allVendors[[1]][1] <- substr(allVendors[[1]][1], 3, nchar(allVendors[[1]][1]))
  allVendors[[1]][number] <- substr(allVendors[[1]][number], 1, nchar(allVendors[[1]][number]) - 2)
  fullOverlapList <- append(fullOverlapList, allVendors[[1]])
}

cleanOverlapList <- gsub("[[:punct:]]", "", fullOverlapList)
cleanOverlapList <- gsub("\r", "", cleanOverlapList)
cleanOverlapList <- gsub("\n", "", cleanOverlapList)
```

# Get Counts by Vendor

```{r}
vendorFrame <- data.frame(Vendor = cleanOverlapList)

organization <- vendorFrame |>
  group_by(Vendor) |>
  summarise(Instances = n()) |>
  arrange(desc(Instances))

organization
```



# Import the Partial Overlap Set

```{r}
partialOverlap <- read_excel('OUP Titles with Partial Overlap with Other Vendors.xlsx')

partialOverlap
```



# Clean Up the Partial Overlap Data:


## The Target Set

```{r}
partOverlapList <- vector()

for(i in 1:dim(partialOverlap)[1]){
  allVendors <- strsplit(partialOverlap$`Interface - Target Set`[i], split = '\n\n', fixed = TRUE)
  number <- length(allVendors[[1]])
  
  allVendors[[1]][1] <- substr(allVendors[[1]][1], 3, nchar(allVendors[[1]][1]))
  allVendors[[1]][number] <- substr(allVendors[[1]][number], 1, nchar(allVendors[[1]][number]) - 2)
  partOverlapList <- append(partOverlapList, allVendors[[1]])
}

cleanOverlapList2 <- gsub("[[:punct:]]", "", partOverlapList)
cleanOverlapList2 <- gsub("\r", "", cleanOverlapList2)
cleanOverlapList2 <- gsub("\n", "", cleanOverlapList2)


cleanOverlapList2
```


## The Target Coverage



```{r}
partOverlapCoverage <- vector()

for(i in 1:dim(partialOverlap)[1]){
  allVendors <- strsplit(partialOverlap$`Coverage - Target Set`[i], split = '\n\n', fixed = TRUE)
  number <- length(allVendors[[1]])
  
  allVendors[[1]][1] <- substr(allVendors[[1]][1], 3, nchar(allVendors[[1]][1]))
  allVendors[[1]][number] <- substr(allVendors[[1]][number], 1, nchar(allVendors[[1]][number]) - 2)
  partOverlapCoverage <- append(partOverlapCoverage, allVendors[[1]])
}

cleanOverlapCoverage <- gsub("[[:punct:]]", "", partOverlapCoverage)
cleanOverlapCoverage <- gsub("\r", "", cleanOverlapCoverage)
cleanOverlapCoverage <- gsub("\n", "", cleanOverlapCoverage)
```


## The Target Embargo Periods

```{r}
partOverlapEmbargo <- vector()

for(i in 1:dim(partialOverlap)[1]){
  allVendors <- strsplit(partialOverlap$`Embargo - Target Set`[i], split = '\n\n', fixed = TRUE)
  number <- length(allVendors[[1]])
  
  allVendors[[1]][1] <- substr(allVendors[[1]][1], 3, nchar(allVendors[[1]][1]))
  allVendors[[1]][number] <- substr(allVendors[[1]][number], 1, nchar(allVendors[[1]][number]) - 2)
  partOverlapEmbargo <- append(partOverlapEmbargo, allVendors[[1]])
}

cleanOverlapEmbargo <- gsub("[[:punct:]]", "", partOverlapEmbargo)
cleanOverlapEmbargo <- gsub("\r", "", cleanOverlapEmbargo)
cleanOverlapEmbargo <- gsub("\n", "", cleanOverlapEmbargo)
```



## The Target Portfolio IDs


```{r}
partOverlapID <- vector()

for(i in 1:dim(partialOverlap)[1]){
  allVendors <- strsplit(partialOverlap$`Portfolio ID - Target Set`[i], split = '\n\n', fixed = TRUE)
  number <- length(allVendors[[1]])
  
  allVendors[[1]][1] <- substr(allVendors[[1]][1], 3, nchar(allVendors[[1]][1]))
  allVendors[[1]][number] <- substr(allVendors[[1]][number], 1, nchar(allVendors[[1]][number]) - 2)
  partOverlapID <- append(partOverlapID, allVendors[[1]])
}

cleanOverlapID <- gsub("[[:punct:]]", "", partOverlapID)
cleanOverlapID <- gsub("\r", "", cleanOverlapID)
cleanOverlapID <- gsub("\n", "", cleanOverlapID)
```



## Target Publication Name List


```{r}
partOverlapName <- vector()

for(i in 1:dim(partialOverlap)[1]){
  allVendors <- strsplit(partialOverlap$`Portfolio ID - Target Set`[i], split = '\n\n', fixed = TRUE)
  number <- length(allVendors[[1]])
  for(j in 1:number){
      partOverlapName <- append(partOverlapName, partialOverlap$Title[i])
  }

}

cleanOverlapName <- gsub("[[:punct:]]", "", partOverlapName)
cleanOverlapName <- gsub("\r", "", cleanOverlapName)
cleanOverlapName <- gsub("\n", "", cleanOverlapName)
```



## Combine Columns


```{r}
partials <- data.frame(Name = cleanOverlapName, 
                       Portfolio_ID = cleanOverlapID, 
                       Platform = cleanOverlapList2, 
                       Coverage = cleanOverlapCoverage, 
                       Embargo = cleanOverlapEmbargo)

partials
```


## Filter Down to the Active Subscriptions

```{r}
currentPartials <- partials |>
  filter(Embargo == '') |>
  filter(str_detect(Coverage, 'until') == FALSE) |>
  filter(Coverage != '')

currentPartials
```



## Find Where the Partials are Located


```{r}
partialLocations <- currentPartials |>
  group_by(Platform) |>
  summarise(Occurrences = n()) |>
  arrange(desc(Occurrences))

partialLocations
```


# Import Usage Data Folder


```{r}
externalUsage <- data.frame()

otherVendorCounter <- list.files(pattern = '.tsv', full.names = TRUE)

for(i in 1:length(otherVendorCounter)){
  vendor <- read_tsv(otherVendorCounter[i], skip = 13) 
  
  vendor <- vendor[,1:12] |>
    mutate(Vendor = case_when(
      i == 1 ~ 'BioOne',
      i == 2 ~ 'EBSCOhost',
      i == 3 ~ 'Gale',
      i == 4 ~ 'JSTOR',
      i == 5 ~ 'OUP',
      i == 6 ~ 'Project Muse',
      i == 7 ~ 'Wiley',
      .default = NA
    ))
  
  externalUsage <- rbind(externalUsage, vendor)
}

dim(externalUsage)
```



```{r}
oupUsage <- externalUsage |>
  filter(Vendor == 'OUP') |>
  mutate(Print_ISSN = gsub('-', '', Print_ISSN),
         Online_ISSN = gsub('-', '', Online_ISSN))

otherUsage <- externalUsage |>
  filter(Vendor != 'OUP') |>
  mutate(Print_ISSN = gsub('-', '', Print_ISSN),
         Online_ISSN = gsub('-', '', Online_ISSN))
```



# Separate the ISSN Data from Alma


```{r}
fullOverlapList2 <- vector()
partialOverlapList2 <- vector()

for(i in 1:dim(overlap)[1]){
  allVendors <- strsplit(overlap$`ISSN(Matching Identifier)`[i], split = '\r\n\r\n', fixed = TRUE)
  fullOverlapList2 <- append(fullOverlapList2, allVendors)
}

for(i in 1:dim(partialOverlap)[1]){
  allVendors <- strsplit(partialOverlap$`ISSN(Matching Identifier)`[i], split = '\n\n', fixed = TRUE)
  partialOverlapList2 <- append(partialOverlapList2, allVendors)
}

issnList <- unlist(c(fullOverlapList2,partialOverlapList2), use.names = FALSE)

fullOverlapList2 <- unlist(fullOverlapList2)
partialOverlapList2 <- unlist(partialOverlapList2)
```


# Filter the Usage Down to Only Overlapped Titles


```{r}
filterOUP <- oupUsage |>
  filter(Print_ISSN %in% issnList | Online_ISSN %in% issnList) |>
  filter(Metric_Type == 'Unique_Item_Requests')

filterOthers <- otherUsage |>
  filter(Print_ISSN %in% issnList | Online_ISSN %in% issnList) |>
  filter(Metric_Type == 'Unique_Item_Requests')
```




# Fill in ISSN Gaps for Summarization

```{r}
joined <- rbind(filterOUP, filterOthers) |>
  mutate(Online_ISSN = case_when(
          Title == 'MELUS' ~ '19463170',
          Title == 'BioScience'~ '15253244',
          Title == 'The English Historical Review' ~ '14774534',
          Title == 'OAH Magazine of History' ~ '19382340',
          Title == 'Biology of Reproduction' ~ '15297268',
          Title == 'Journal of Church and State' ~ '20404867',
          Title == 'Political Science Quarterly' ~ '1538165X',
          Title == 'Social Work' ~ '15456846',
          Title == 'Social Work Research' ~ '15456838',
          Title == 'Essays in Criticism' ~ '14716852',
          Title == 'Journal of Economic Entomology' ~ '1938291X',
          Title == 'Notes and Queries' ~ '14716941',
          Title == 'The British Journal of Aesthetics' ~ '14682842',
          .default = Online_ISSN)
  )
```





# Pivot the Usage Data Wider


```{r}
comparison <- joined |>
  mutate(oupUsage = ifelse(Vendor == 'OUP', Reporting_Period_Total, 0),
         bioOneUsage = ifelse(Vendor == 'BioOne', Reporting_Period_Total, 0),
         EBSCOUsage = ifelse(Vendor == 'EBSCOhost', Reporting_Period_Total, 0),
         galeUsage = ifelse(Vendor == 'Gale', Reporting_Period_Total, 0),
         JSTORUsage = ifelse(Vendor == 'JSTOR', Reporting_Period_Total, 0),
         museUsage = ifelse(Vendor == 'Project Muse', Reporting_Period_Total, 0),
         wileyUsage = ifelse(Vendor == 'Wiley', Reporting_Period_Total, 0))

comparison
```



# Usage Summary


```{r}
usageBreakdown <- comparison |>
  group_by(Online_ISSN) |>
  summarize(numVendors = n(),
            allUsage = sum(Reporting_Period_Total),
            maxUsage = max(Reporting_Period_Total),
            oupUsage = max(oupUsage),
            bioOneUsage = max(bioOneUsage),
            EBSCOUsage = max(EBSCOUsage),
            galeUsage = max(galeUsage),
            JSTORUsage = max(JSTORUsage),
            museUsage = max(museUsage),
            wileyUsage = max(wileyUsage)) |>
  mutate(nonOUPUsage = allUsage - oupUsage,
         topVendor = case_when(
          maxUsage == oupUsage ~ 'OUP',
          maxUsage == bioOneUsage ~ 'BioOne',
          maxUsage == EBSCOUsage ~ 'EBSCO',
          maxUsage == galeUsage ~ 'Gale',
          maxUsage == JSTORUsage ~ 'JSTOR',
          maxUsage == museUsage ~ 'Project Muse',
          maxUsage == wileyUsage ~ 'Wiley',
          .default = 'None'
        )) |>
  mutate(oupRate = round(100.0*(oupUsage / allUsage),1),
         nonOUPRate = round(100.0*(nonOUPUsage / allUsage),1)) |>
  filter(numVendors > 1) |>
  mutate(overlapType = case_when(
    Online_ISSN %in% partialOverlapList2 & !Online_ISSN %in% fullOverlapList2 ~ 'Partial',
    Online_ISSN %in% fullOverlapList2 ~ 'Full',
    .default = 'Unknown'
  ))


usageBreakdown
```


```{r}
issnList2 <- unique(usageBreakdown$Online_ISSN)
titles <- c()

for(i in 1:length(issnList2)){
  titles <- append(titles, comparison[comparison$Online_ISSN == issnList2[i],]$Title[1])
}

fullBreakdown <- cbind(usageBreakdown, titles)

fullBreakdown
```



```{r}
test <- fullBreakdown |>
  group_by(Online_ISSN) |>
  summarise(n = n()) |>
  arrange(desc(n))

test
```


# Create Dataset: Names of Journals Where OUP is not Most Used


```{r}
notOUP <- fullBreakdown |>
  filter(topVendor != 'OUP') |>
  select(titles, Online_ISSN, overlapType, allUsage, topVendor, maxUsage, oupUsage)

colnames(notOUP) <- c('Title', 'Online ISSN', 'Full or Partial Overlap', 'All Usage', 'Top Vendor', 'Top Vendor Usage', 'OUP Usage')

notOUP
```


```{r}
write.csv(notOUP, 'OUP Overlap Used More by Other Vendor.csv')
```


# Make Visuals: Pie Chart of Top Vendor


```{r}
topVendorBreakdown <- fullBreakdown |>
  group_by(overlapType, topVendor) |>
  summarize(n = n()) |>
  arrange(desc(n)) |>
  mutate(topVendor = factor(topVendor, levels = c('OUP', 'JSTOR', 'Wiley', 'EBSCO')))

topVendorBreakdown
```



```{r}
ggplot(topVendorBreakdown |>
         filter(overlapType == 'Full')
       , aes(x = '', y = n, fill = topVendor)) +
  geom_col() +
  coord_polar(theta = "y") +
  geom_label(aes(label = n),
             color = 'white',
             position = position_stack(vjust = 0.4),
             show.legend = FALSE) +
  scale_fill_manual(values = c('#117733', '#44aa99', '#882255', '#ddcc77')) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "#ffffff"),
        plot.background = element_rect(fill = "#ffffff"),
        legend.background = element_rect(fill = "#ffffff")) +
  ggtitle('Most-Used Vendors of Fully Overlapped Titles') +
  guides(fill = guide_legend(title = 'Top Usage Vendor'))
```



# Make Visuals: OUP Usage Plotly


```{r, warning = FALSE}
palette <- c('#4b4b4b', '#ff8200')

fullBreakdown <- fullBreakdown |>
  mutate(oupTop = ifelse(topVendor == 'OUP', 'Yes', 'No'))

plotlyTrend <- plot_ly(data = fullBreakdown, x = ~oupRate, y = ~allUsage, color = ~oupTop, colors = palette,
                       marker = list(size = 10),
                       text = ~paste('<b>Title:', titles, '<br><b>Most Used Vendor:', topVendor, '<br><b>Overlap Type:', overlapType)) |>
  layout(title = '<b> % of Total Usage on OUP for Overlap Titles',
         yaxis = list(zeroline = FALSE, title = '<b>Total Usage since Jan-2022'),
         xaxis = list(zeroline = FALSE, title = '<b>% Usage from OUP'),
         legend = list(title = list(text = '<b> Is OUP <br> Top Vendor?')),
         autosize = FALSE,
         width = 800,
         height = 500)


# 1100 and 850 are better for saving to HTML
## 800 and 500 are better for viewing in RStudio

plotlyTrend

#htmltools::save_html(plotlyTrend, 'Total Usage and OUP Percentage.html')
```




# Make Visuals: GT Table, Which Vendors Overlap with OUP the Most?


```{r}
cleanOrg <- organization |>
  filter(Instances >= 10)

cleanOrg
```



```{r}
overlapTable <- cleanOrg |>
  gt() |>
  tab_header(title = md('**Vendors with Greatest Overlap with OUP**')) |>
  cols_align(align = 'center', columns = c('Vendor', 'Instances')) |>
  opt_stylize(style = 5, color = 'blue') |>
  cols_label(Instances = '# Overlaps') |>
  cols_width(Vendor ~ px(250), everything() ~ px(125)) |>
  opt_table_font(
    font = 'rounded-sans',
    size = 14
  )

overlapTable
```

